Evolution of Processes in Delivering Reliable Software within the European Scientific Arena

### 2019-02-14 paper-jgc.tex
Add SQA baseline GitHub repo reference

The SQA criteria are a set of conventions and recommendations that pave the way for
the adequate development, timely delivery and reliable operation of the produced software components.
They emphasize the quality requirements and best practices to be applied at the
development phase, such as style and testing compliance or human code reviews, to protect the
production source code versions. Furthermore, the criteria promote the adoption of the software
by providing minimum requirements of documentation content and stressing the usage of automated
solutions for software deployment. The SQA criteria are continuously evolving \cite{sqa-baseline}, aiming at serving
as a reference for future software development projects within the European research ecosystem.

@@

>>>>

The SQA criteria are a set of conventions and recommendations that pave the way for
the adequate development, timely delivery and reliable operation of the produced software components.
They emphasize the quality requirements and best practices to be applied at the
development phase, such as style and testing compliance or human code reviews, to protect the
production source code versions. Furthermore, the criteria promote the adoption of the software
by providing minimum requirements of documentation content and stressing the usage of automated
solutions for software deployment. The SQA criteria are publicly available \cite{sqa-baseline} and
it is continuously evolving by means of an open collaboration procedure \cite{sqa-baseline-repo}
that aims at serving as a reference for quality assurance realization in research software.

@@

\bibitem{sqa-baseline-repo}
Members of the INDIGO-DataCloud, DEEP Hybrid-DataCloud and eXtreme DataCloud collaborations, 2015-2020,
``A set of Common Software Quality Assurance Baseline Criteria for Research Projects,''
2018.
[Online]. Available: \url{https://github.com/indigo-dc/sqa-baseline}
[Accessed 14 Feb. 2019].
